Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 lower_bound.tex
addressed some comments

We saw in Corollary~\ref{cor:constant-regret} that
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that the regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.

@@

Because a pull of arm $(0,1)$ is observed in each time step,
after $t$ rounds, the estimate \ArmEV{t}{(0,1)} is of the form
$(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
where $\Noise[t]{1} \sim \Normal{0}{\sqrt{1/t}}$
and $\Noise[t]{2} \sim \Normal{0}{\sqrt{1/t}})$.
\dkcomment{I think we define this to be the estimates at the beginning
  of round $t$, so we may be off by 1 here and in other places.}
We lower-bound the regret in step $t$ by focusing on the event that
both normal noise coordinates are non-negative,
which by symmetry has probability \quarter:

>>>>

We saw in Corollary~\ref{cor:constant-regret} that \bccomment{David, could you put the right reference here?}
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that the regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.

@@

Because a pull of arm $(0,1)$ is observed in each time step,
after $t$ rounds, the estimate \ArmEV{t}{(0,1)} is of the form
$(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
where $\Noise[t]{1} \sim \Normal{0}{\sqrt{1/t}}$
and $\Noise[t]{2} \sim \Normal{0}{\sqrt{1/t}})$.
We lower-bound the regret in step $t$ by focusing on the event that
both normal noise coordinates are non-negative,
which by symmetry has probability \quarter:

### 2018-02-16 payment-proof.tex
fixed some typos
addressed some comments

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
\dkcomment{Copy here the final form of the theorem once it is finalized.}
\end{rtheorem}

@@

To reason about such estimation errors formally, we define
\emph{envelopes} of sample paths.
A sample path \SP captures all the random events affecting the
algorithm, i.e., the random draws \AgentV{t} of agents and the
noise \NoiseV[t] in the draws the pulled arms,
with an infite \dkcomment{Is it infinite?} time horizon.
\dkcomment{We should be consistent about using filtration vs.~sample
  path.}
\pfcomment{I removed discussion of filtrations and replaced them by discussion of history.}

@@

\begin{align*}
\hat{L}_\ell
  & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j,t},\\
\Env{1} & = \hat{L}_1\\ 
\Env{\ell} & = \hat{L}_{\ell} - \hat{L}_{\ell-1}
  \qquad \mbox{ for } \ell \geq 2.
\end{align*}

@@

\begin{lemma} \label{lem:sample-path-payment}
If $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, then
the payment in step $t$ is upper-bounded by
$\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
\dkcomment{Verify that the way I talk about $t$ vs.~$s$ is right.}
\end{lemma}

@@

Let the random stopping time $\tau_{i,j}$ be the first value of
\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
$h(\NumPull{t}{i})$.
We apply Lemma~\ref{lem:ACI-inequality}
to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
with $b(n) = (\ell-1)^2$ \dkcomment{omit dependence on $n$ here?}.
We obtain that the probability that $\tau_{i,j} < \infty$ and 
$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
$12 \e^{-1.8 b(n)}$.
By definition of $\tau_{i,j}$, the event is the same as simply
$\tau_{i,j} < \infty$.
Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
and taking a union bound over both cases,
gives us that the probability that there is \emph{any} time $t$ with
$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
is at most $24 \e^{-1.8 b(n)}$.
Hence, the probability that the error at \emph{any} time $t$ exceeds
$g(s(t,\SP), \ell-1)$ is bounded by 
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

@@

\begin{align*}
O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
& = 
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
\cdot \exp(\frac{2}{\MinProb}) \right).
\end{align*}
\dkcomment{$p^{-5/2}$ is dominated by $\exp(2/p)$.}
\pfcomment{the bound got tighter.  I didn't carry this forward anywhere where we report on / use the bound.}
\end{extraproof}

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:budget}}
The payment budget for Algorithm~\ref{alg:basic-incentivizing} is bounded above by 
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right).  \nonumber 
\end{align}
\end{rtheorem}

@@

To reason about such estimation errors formally, we define
\emph{envelopes} of sample paths.
A sample path \SP captures all the random events affecting the
algorithm, i.e., the random draws \AgentV{t} of agents and the
noise \NoiseV[t] in the draws the pulled arms,
with an infinite time horizon.

@@

\begin{align*}
\hat{\mathcal{L}}_\ell
  & = \Set{\SP}{|\Err{t}{i}{j}(\SP)| \leq g(s(t,\SP),\ell)
    \mbox{ for all } i,j,t},\\
\Env{1} & = \hat{\mathcal{L}}_1,\\ 
\Env{\ell} & = \hat{\mathcal{L}}_{\ell} \setminus \hat{\mathcal{L}}_{\ell-1}
  \quad \mbox{ for } \ell \geq 2.
\end{align*}

@@

\begin{lemma} \label{lem:sample-path-payment}
If $\SP \in \Env{\ell}$ and $s(t,\SP) = s$, then
the payment in step $t$ is upper-bounded by
$\bar{c} (s,\ell) = \MAXR + 2 \Diam d \cdot g(s,\ell)$.
\end{lemma}

@@

Let the random stopping time $\tau_{i,j}$ be the first value of
\NumPull{t}{i} (i.e., the first pull of arm $i$) such that 
$S_{i,j}(\tau_{i,j}) > h(\NumPull{t}{i})$.
$\tau_{i,j} = \infty$ means that the estimation error never exceeds 
$h(\NumPull{t}{i})$.
We apply Lemma~\ref{lem:ACI-inequality}
to $S_{i,j}(t)$, with a stopping time of $\tau_{i,j}$ and
with $b = (\ell-1)^2$.
We obtain that the probability that $\tau_{i,j} < \infty$ and 
$S_{i,j}(\tau_{i,j}) > h(\tau_{i,j})$ is at most
$12 \e^{-1.8 b}$.
By definition of $\tau_{i,j}$, the event is the same as simply
$\tau_{i,j} < \infty$.
Applying the lemma again to $-S_{i,j}(\tau_{i,j})$,
and taking a union bound over both cases,
gives us that the probability that there is \emph{any} time $t$ with
$|S_{i,j}(\NumPull{t}{i})| > h (\NumPull{t}{i})$
is at most $24 \e^{-1.8 b(n)}$.
Hence, the probability that the error at \emph{any} time $t$ exceeds
$g(s(t,\SP), \ell-1)$ is bounded by 
\begin{align*}
\Prob{|\Err{t}{i}{j}| \geq g(s(t,\SP), \ell-1)}
& \leq 24 \e^{-1.8(\ell-1)^2}.
\end{align*}
Now, taking a union bound over all arms $i$ and
coordinates $j$ completes the proof.

@@

\begin{align*}
O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right)
& = 
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma
\cdot \exp(\frac{2}{\MinProb}) \right).
\end{align*}
\end{extraproof}

### 2018-02-16 problem_setting.tex
minor edits
addressed some comments

We consider a MAB setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, but unknown to the agents
or the principal.
Whenever arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero \pfedit{independent} 
Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps. This is not material for
  the analysis.}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
\dkcomment{Clarify if we can handle more general noise.}
Here, $I_d$ denotes the $d \times d$ identity matrix.

@@

\dkcomment{Do we need this definition here?}\pfcomment{I agree that we can move the definition of phase to where we define our algorithm.}
We call time $t_{n}=\min_{t}\{\forall i, \NumPull{t}{i} \geq n\}$ the
\emph{starting point of the $n^{th}$ phase}.
We call the set of times $[t_{n}, t_{n+1})$ the
\emph{$n^{th}$ round}.

>>>>

We consider a MAB setting with \ARMNUM arms.
Arm payoffs are determined by $d$ \emph{attributes} or \emph{features};
hence, arms can be identified with vectors $\ArmV{i} \in \R^d$.
The \ArmV{i} are (adversarially) fixed, but unknown to the agents
or the principal.
Whenever arm $i$ is pulled, its current utility-relevant features are
determined as $\ArmV{i} + \NoiseV$, where \NoiseV is a mean-zero independent Gaussian%
\footnote{For simplicity of notation, we assume that the variance
  $\sigma^2$ is uniform across time steps. This is not material for
  the analysis.}
noise vector $\NoiseV \sim \Normal{\vc{0}}{\sigma^2 I_{d}}$.
\dkcomment{Clarify if we can handle more general noise.}
Here, $I_d$ denotes the $d \times d$ identity matrix.

@@
